### 2015-11-17 drafts/hybrid_zone.tex
took a stab at writing some intro

\section{Introduction}
-Studying hybrid zones is a great opportunity to understand the maintenance of distinct species, and the process of speciation. Here we consider hybrid zones that are a cline that is maintained by selection against hybrids (so-called tension zone). \\
-Gene flow across a hybrid zone may be impeded by selection against migrants. In older contact zones, loci that are associated with reduced fitness in heterozygotes will have steeper clines than the rest of the genome. There is probably a lot to learn from geographic patterns at loci neighboring selected loci (e.g. small block lengths indicate that there has been plenty of opportunity for recombination in heterozygous backgrounds)\\ 
-There has been a lot of investigation into the equilibrium state of hybrid zones, at both selected and linked loci. \\
-We consider the non-equilibrium state of hybrid zones, and patterns of linkage around selected loci. This will become increasingly relevant as studiers of HZs get genomic data and can reliably estimate block lengths. \\

>>>>

\section{Introduction}
The process of speciation often involves allopatric divergence in relative isolation. When formerly isolated populations come back into contact, a hybrid zone can form, and may be maintained stably by selection. In such instances, selection on some subset of the genome prevents mixing of genotypes between species. We refer to such hybrid zones as tension zones (as opposed to contact zones which reflect a non-equilibrium gradient in ancestry that will eventually be eroded by migration throughout the whole genome). Because the population genetic signatures around loci experiencing selection is going to differ from other regions of the genome, natural hybrid zones present exciting opportunities to understand species maintenance and the process of speciation.\\

Gene-flow across a hybrid zone is impeded by selection against migrant, or hybrid, genotypes, and as a result, produces a cline in ancestry that is expected to be steepest at and nearby the selected locus. Elsewhere in the genome, clines in ancestry are wider, and are more heavily influenced by hybrid zone age and rates of migration. Historically, this has been the most relied-upon population genetic signature, and it is only recently that abundant genomic data has opened the possibility of studying patterns of linkage within hybrid zones. For example, patterns of linkage disequilibrium (LD) or tract length distribution across geographic space can provide information about zone age \cite{Sedghifar2015}. In tensions zones geographic patterns of linkage at loci neighboring targets of selection can potentially be a powerful source of information.\\

Many of the traditional models of genetic variation in hybrid zones to date have focused on the equilibrium state of hybrid zones, at both selected and linked loci (lots of Barton).

%-Studying hybrid zones is a great opportunity to understand the maintenance of distinct species, and the process of speciation. Here we consider hybrid zones that are a cline that is maintained by selection against hybrids (so-called tension zone). \\
%-Gene flow across a hybrid zone may be impeded by selection against migrants. In older contact zones, loci that are associated with reduced fitness in heterozygotes will have steeper clines than the rest of the genome. There is probably a lot to learn from geographic patterns at loci neighboring selected loci (e.g. small block lengths indicate that there has been plenty of opportunity for recombination in heterozygous backgrounds)\\ 
%-There has been a lot of investigation into the equilibrium state of hybrid zones, at both selected and linked loci. \\
-We consider the non-equilibrium state of hybrid zones, and patterns of linkage around selected loci. This will become increasingly relevant as studiers of HZs get genomic data and can reliably estimate block lengths. \\
